\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Swapnil}{Dey}{ \urlstyle{same}\href{https://techswappy.github.io/}{https://techswappy.github.io}\\
\href{mailto:swapnildey94@gmail.com}{Email Me}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Jadavpur University}
\descript{Bachelors in Construction Engg.}
\location{June 2016 | Kolkata, IND}
\sectionsep

\subsection{Delhi Public School}
\descript{Ruby Park | Kolkata, IND}
\location{May 2012}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/techswappy}{\bf techswappy} \\
LinkedIn://  \href{https://www.linkedin.com/in/swapnildey}{\bf swapnildey} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{}   Javascript \textbullet{} HTML5 \textbullet{} Python \\
\location{Frameworks:}
Android \textbullet{}   AngularJS \textbullet{} Flask \textbullet{} Spring \\
\location{Familiar:}
AWS \textbullet{} iOS \textbullet{} Sybase \textbullet{} IBM DB2 \\
MongoDB \textbullet{} API Management \textbullet{} OAuth 2.0 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\runsubsection{Goldman Sachs}
\descript{| Associate Software Engineer }
\location{Jan 2019 - Present | Bengaluru, IND}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developing key solutions for the client portal that helps to deliver financial wellness knowledge to institution members.
\item Working on critical solutions targeted at Retail consumers.
\item \href{https://in.reuters.com/article/goldman-sachs-consumer-brokerage/after-years-serving-ceos-goldmans-ayco-also-wants-other-workers-idINL1N21M22J}{\bf Media Coverage}
\end{tightemize}
\sectionsep

\section{Experience}
\runsubsection{Goldman Sachs}
\descript{| Software Engineer }
\location{Jun 2016 - Dec 2018 | Bengaluru, IND}
\begin{tightemize}
\item Work with Business teams to develop Web Applications and Micro Services to help implement innovative solutions which can cater to regulatory measures or business value addition.
\item Developed productivity solutions for Financial Advisers to help them manage their client meeting letters. It was one of the first report based speech to text solutions in the firm.
\end{tightemize}
\sectionsep

\runsubsection{CUREGATEWAY}
\descript{| Consultant | Medical Start-up }
\location{Dec 2015 – Jun 2016 | Kolkata, IND}
\begin{tightemize}
\item Worked on publicly collected Data of Hospitals \& Doctors to link them with Diseases and Treatments.
\item Developed Medical Planning Tool to help Medical Tourists select options - across Mumbai, Kolkata \& Bengaluru across three segments of Hospitals on the basis of Cost and Quality of treatment.
\item Application went viral on Playstore with top reach in Bangladesh, Sri Lanka \& Nepal
\end{tightemize}
\sectionsep

\runsubsection{HILTI INDIA PVT. LTD.}
\descript{| Intern | Marketing }
\location{Jun 2015 – Aug 2015 | New Delhi, IND}
\begin{tightemize}
\item Migration of Strategic Marketing data on the SAP CRM platform
\item Mobile App for easy upload of CRM Leads into SAP Cloud
\item App for Sales team to highlight approx delivery time based on inputs from Supply Chain team
\end{tightemize}
\sectionsep

\runsubsection{INMEDITECH LLP}
\descript{| CO-FOUNDER \& APPLICATION DEVELOPER}
\location{Jun 2014 – Nov 2014 | Bengaluru \& New Delhi, IND}
\begin{tightemize}
\item Developed wearable device for Pregnant \& Married woman in Rural areas to increase their visit to PHCs for ANC
\item Built unique cloud solution for villagers \& healt workers accessible using SMS
\item Product was recognized \& sponsored by CAMTech India, FICCI \& Terumo India
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2016	     & University  & Best All Rounder Graduate - Batch of 2016, Jadavpur University\\
2013     & National & 12\textsuperscript{th} Youth Parliament under Government of India  \\
2014	     & National  & CAMTech India Medical Hackathon\\
2014	     & National  & FICCI Heal 2014 Medical Innovation of the Year\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
